He-Man: A domain-specific language for lightweight concurrency

### 2011-12-13 report/report.tex
Write a bad abstract

\begin{abstract}
TODO
\end{abstract}

>>>>

\begin{abstract}
We present He-Man, a Haskell compiled, embedded, domain specific
language for building scalable network applications in a natural,
straight-line manner while still emitting efficient event-loop based
code. He-Man programs are compact and measurements indicate that it
performs acceptably. 
\end{abstract}
